\documentclass{conm-p-l}

\usepackage{macros}

\newtheorem{theorem}{Theorem}[section]
\newtheorem{lemma}[theorem]{Lemma}

\theoremstyle{definition}
\newtheorem{definition}[theorem]{Definition}
\newtheorem{example}[theorem]{Example}
\newtheorem{xca}[theorem]{Exercise}

\theoremstyle{remark}
\newtheorem{remark}[theorem]{Remark}

\numberwithin{equation}{section}



\def\brian{\textcolor{blue}{BW: }\textcolor{blue}}
\def\owen{\textcolor{red}{OG: }\textcolor{red}}

\renewcommand{\contentsname}{}

\begin{document}

\title{The holomorphic bosonic string}

\author{Owen Gwilliam}
\address{Max Planck Institute for Mathematics, Bonn, Germany}
\email{gwilliam@mpim-bonn.mpg.de}
%\thanks{}

\author{Brian Williams}
\address{Department of Mathematics, Northwestern University, Evanston, IL}
\subjclass[2010]{Primary 81T30, 81T70, Secondary 58D27, 17B69}

\date{}

\begin{abstract}
\owen{I modestly rewrote. Let me know what you think.}
We describe and analyze a holomorphic version of the bosonic string in the formalism of quantum field theory developed by Costello and collaborators, which provides a powerful combination of renormalization theory and the Batalin-Vilkovisky formalism. Our focus here is on the case in which the target space-time is a vector space. We identify the critical dimension as an obstruction to satisfying the quantum master equation, and when the obstruction vanishes, we construct a one-loop exact quantization. Moreover, we show how the factorization algebra of observables recovers the BRST cohomology of the string and use this perspective to give a new construction of its Gerstenhaber structure. Finally, we show how the factorization homology along closed manifolds encodes the determinant line bundle over the moduli space of Riemann surfaces.
An auxiliary goal of this paper is to give an exposition of this QFT formalism with the holomorphic bosonic string theory as the running example.
\end{abstract}

\maketitle


%\section*{Contents}
\setcounter{tocdepth}{1}

\tableofcontents


\input{bvoverview}
\input{classicaltheory}
\input{moduli}
\input{quantization}
\input{vertexalgebra}
\input{conformalblock}
\input{curvedtargets}
\input{calc}

\bibliographystyle{amsalpha}

\bibliography{string}

\end{document}